# Missing values
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(patchwork)
source("missing_func.R")
```

## Motorcycle Accident Missing Pattern
We will focus on the motorcycle accident data to provide a clear missing pattern with explaination.


```{r, echo = F, message=F}
df <- read.csv("clean_data.csv", stringsAsFactors = F)
```


```{r, echo = F, message=F, fig.width=8, fig.height=8}
collision_2021_11_Plot <- plot_missing(df, FALSE)
collision_2021_11_Plot
```

We summarize this November-2021 data to provide a sufficient and recognizable missing pattern. 

For better understanding， I will explain significant missing variables there.

Column Name| Meaning
------------- | -------------
vehicle_type_code_# |  the type of vehicle based on the selected vehicle category (ATV, bicycle, car/suv, ebike, escooter, truck/bus, motorcycle, other)
contributing_factor_vehicle_# | the factor contributing to the collision for designated vehicle
on_street_name |the street on which the collision occurred
cross_street_name | Nearest cross street to the collision
off_street_name | Street address if known

After data cleaning, our most representative missing pattern now are accidents without having data lack of value for 'cross_street_name'.

As cross_street, on_street, and off_street are categorical variables that are not essential for our borough discussion, the column data value with lacking cross_street_name represent that most accidents occur on_street or has a specific street location in off_street. That means most motor accidents occurs on streets instead of road intersections. The second missing pattern of on_street and off_street represents all accidents that happends at road intersections.

The third missing pattern are vehicle collisions happen with on_street location variable. That kind of accidents involves street like expressway that are not distributed to any borough or zipcode region.

From column perspetive, we could see that most accidents do not have more than 2 vehicles. With on_street or off_street collision appear more often than cross_street collision.

Column and row frequency shares similarity to provide the real accident phenomenon and tell us which type of accident appears more frequently. Missing pattern analysis provide sufficient details for what features most motorcycle collisions would have and what are other common features that motorcycle collisions shares sorting by pattern frequency.

